### 2019-06-18 initial/notes.tex
Toy Problem 2 seems solved

Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
$\mathcal{C}_i$.

>>>>

Thus, in our toy model, we \emph{cannot} choose a simple form e.g.\
$\rd{\alpha}{t} = -\epsilon\alpha$, it must have differing signs over
$\mathcal{C}_i$. Let's consider a model where $\dot{\eta} = +\epsilon \eta \mu$.
It should be noted that, upon careful calculation, $\dot{\eta} = -\epsilon \eta
\mu$ will \emph{not} result in any captures! Our choice only permits captures
\emph{from top down}. We will see this below.

Our expression then becomes:
\begin{align*}
    B_i &= \int -\frac{\epsilon \mu}{2\alpha^2}\s*{
        \alpha^2 \mu^2 - \cos^2 I}\;\mathrm{d}t,\\
        &\approx -\frac{\epsilon}{2\alpha^2} \int
            \mu \frac{\alpha^2 \mu^2 - \cos^2 I}{
                -\alpha \mu + \cos I}\;\mathrm{d}\phi,\\
        &\approx +\frac{\epsilon}{2\alpha^2}\int
            \mu\p*{\alpha \mu + \cos I}\;\mathrm{d}\phi.
\end{align*}
Now, we can evaluate our two integrals. For some reason my usual arguments
(taking symmetric/antisymmetric part etc.) don't seem to do too well here, there
are too many terms, so we will keep as many terms as possible.

First, we tackle the top integral. Here, the integrand is evaluated at
$\mu_+(\phi) = \eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$, so we can
plug this in and compute
\begin{align*}
    B_{top}\frac{2\alpha^2}{\epsilon} &= \int\limits_{2\pi}^{0}
            \mu(\alpha \mu + \cos I)\;\mathrm{d}\phi,\\
        &= -\int\limits_0^{2\pi}
            \p*{\eta \cos I + \sqrt{2\eta \sin I\p*{1 - \cos \phi}}}
                \p*{2\cos I + \sqrt{2\sin I\p*{1 - \cos \phi}/\eta}}
                \;\mathrm{d}\phi.
\end{align*}
Let's track the four terms in FOIL (first, outer, inner, last) order. (F)
evaluates to just $4\pi \eta \cos^2 I$. (O) evaluates to $\frac{\cos
I}{2}A_{sep} = 8\cos I\sqrt{\eta \sin I}$, and (I) twice that. Lastly, (L)
evaluates to $4\pi \sin I$. This agrees with our numerical check.

We now track the bottom integral. Here, the integrand is instead evaluated at
$\mu_-(\phi) = \eta \cos I - \sqrt{2\eta \sin I\p*{1 - \cos \phi}}$. This flips
the signs of the (O) and (I) terms above. Furthermore, the $\mathrm{d}\phi$
direction changes, and so we arrive at capture probability
\begin{equation}
    P_{c} = \frac{48\cos I \sqrt{\eta \sin I}}{
        4\pi \sin I + 24\cos I \sqrt{\eta \sin I} + 4\pi \eta \cos^2 I}.
\end{equation}
The issue compared to the analytical computation comes in because $\cos I$ gives
an extra factor of $1.5$ to the antisymmetric term, which gives a large enough
prefactor that the $\sqrt{\eta}$ term is competitive with the $\eta^0$ term in
the denominator; my earlier work showed $P_c = \frac{8\cos
I\sqrt{\eta}}{\pi \sqrt{\sin I}}$. The last term in the denominator is
negligible though, as one might expect.
